Interpolation of Sparse High-Dimensional Data\thanks {This work was supported by the National Science Foundation Grant CNS-1565314.}

### 2019-03-20 Paper_[2019-02]_Numerical_Algorithms/paper.tex
Added code to time Delaunay for fit time fix. Updated some report.

The forest fire data set \cite{cortez2007data} describes the area of
Montesinho park burned over months of the year along with
environmental conditions. The twelve dimensions being used to model
burn area are the $x$ and $y$ spatial coordinates of burns in the
park, month of year (mapped to a 2D circle), the FFMC, DMC, DC, and
ISI indices (see source for details), the temperature, relative
humidity, wind speed, and outdoor rain. The original analysis of this
data set demonstrated it to be difficult to model, likely due to the
skew in response values.

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.75\textwidth,]{Figures/raw-histogram-throughput.pdf}};
    \node[below=of img, node distance=1cm, yshift=1cm] {I/O Read Throughtput};
    \node[left=of img, node distance=0cm, rotate=90, anchor=center,yshift=-0.7cm] {Count};
  \end{tikzpicture}
  \caption{Histogram of the raw throughput values recorded during all
    IOzone tests across all system configurations. The distribution is
    skewed right, with few tests having significantly higher
    throughput than most others. The data is presented on a $\ln$
    scale, however the resulting left-skew reveals the data is not
    precisely distributed according to an exponential.}
  \label{fig:hist-throughput}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l}
    Algorithm & \multicolumn{2}{c|}{Avg. \% Best} & \multicolumn{2}{c|}{\multilinecell{Avg. Fit or \\ Prep. Time (s)}} & \multicolumn{2}{c}{Avg. App. Time (s)}\\
    \hline
    MARS & \quad\quad$4$&$6$ & \,\quad$22$&$3$ & \quad\quad$0$&$00137$\\
    SVR & $\mathit{21}$&$\mathit{1}$ & $0$&$503$ & $\mathit{0}$&$\mathit{000137}$\\
    MLP & $\mathbf{42}$&$\mathbf{1}$ & $210$&$0$ & $0$&$00102$\\
    Delaunay & $6$&$0$ & $\mathbf{0}$&$\mathbf{000143}$ & $3$&$03$\\
    ShepMod & $18$&$4$ & $0$&$711$ & $0$&$000149$\\
    LSHEP & $8$&$4$ & $1$&$69$ & $\mathbf{0}$&$\mathbf{000116}$\\
    Voronoi & $0$&$5$ & $\mathit{0}$&$\mathit{127}$ & $0$&$0375$\\
    BoxSplines & $0$&$2$ & $0$&$816$ & $0$&$000526$\\
  \end{tabular}
  \caption{This average of Appendix Tables
    \ref{table:best-forest-fire}, \ref{table:best-parkinsons},
    \ref{table:best-weather}, and \ref{table:best-credit-card}
    provides a gross summary of overall results. The columns display
    (weighted equally by data set, \textit{not} points) the average
    frequency with which any algorithm provided the lowest absolute
    error approximation, the average time to fit / prepare, and the
    average time required to approximate one point. Interpolants
    provide the lowest error approximation one third of the time
    across all data, while regressors occupy the other two
    thirds. This result is obtained without any customized tuning or
    preprocessing to maximize the performance of any given
    algorithm. In practice, tuning and preprocessing may have large
    effects on approximation performance.}
  \label{table:avg-performance}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c|}{Min} & \multicolumn{2}{c|}{$25^{th}$} & \multicolumn{2}{c|}{$50^{th}$} & \multicolumn{2}{c|}{$75^{th}$} & \multicolumn{2}{c}{Max}\\
    \hline
    MARS & $0$&$00948$ & $9$&$98$ & $20$&$4$ & $32$&$9$ & $863$&$0$\\
    SVR & $0$&$00138$ & $3$&$17$ & $7$&$31$ & $12$&$6$ & $\mathbf{27}$&$\mathbf{5}$\\
    MLP & $0$&$0000239$ & $\mathit{0}$&$\mathit{533}$ & $\mathit{1}$&$\mathit{25}$ & $\mathbf{2}$&$\mathbf{84}$ & $39$&$3$\\
    Delaunay & $\mathit{3}$&$\mathit{72 \times 10^{-12}}$ & $1$&$20$ & $3$&$50$ & $7$&$67$ & $30$&$7$\\
    ShepMod & $\mathbf{0}$&$\mathbf{00}$ & $\mathbf{0}$&$\mathbf{255}$ & $\mathbf{0}$&$\mathbf{908}$ & $\mathit{3}$&$\mathit{43}$ & $34$&$5$\\
    LSHEP & $0$&$00254$ & $2$&$93$ & $7$&$16$ & $13$&$1$ & $\mathit{29}$&$\mathit{0}$\\
    Voronoi & $\mathbf{0}$&$\mathbf{00}$ & $1$&$29$ & $3$&$52$ & $6$&$87$ & $30$&$1$\\
    BoxSpline & $0$&$00287$ & $4$&$39$ & $9$&$10$ & $14$&$8$ & $41$&$3$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-parkinsons}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum of each column is boldface, while the second lowest value
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-parkinsons}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \quad\,$0$&$0$ &  & \quad\quad$37$&$9$ & \quad\,\,$0$&$00253$ & \quad\quad\quad\,\,$1$&$48$\\
    SVR & $0$&$1$ &  & $0$&$859$ & $\mathit{0}$&$\mathit{000181}$ & $\mathit{0}$&$\mathit{106}$\\
    MLP & $\mathit{32}$&$\mathit{0}$ &  & $348$&$0$ & $0$&$00111$ & $0$&$653$\\
    Delaunay & $0$&$0$ &  & $\mathbf{0}$&$\mathbf{000190}$ & $3$&$69$ & $2170$&\\
    ShepMod & $\mathbf{66}$&$\mathbf{4}$ &  & $1$&$13$ & $0$&$000182$ & $0$&$107$\\
    LSHEP & $0$&$0$ &  & $2$&$39$ & $\mathbf{0}$&$\mathbf{000144}$ & $\mathbf{0}$&$\mathbf{0845}$\\
    Voronoi & $1$&$6$ &  & $\mathit{0}$&$\mathit{298}$ & $0$&$0274$ & $16$&$1$\\
    BoxSpline & $0$&$0$ &  & $1$&$26$ & $0$&$000643$ & $0$&$377$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating Parkinson's data in Table
    \ref{table:error-parkinsons}. On the right columns are median fit
    time of 5288 points, median time for one approximation, and median
    time approximating 587 points.}
  \label{table:best-parkinsons}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c|}{Min} & \multicolumn{2}{c|}{$25^{th}$} & \multicolumn{2}{c|}{$50^{th}$} & \multicolumn{2}{c|}{$75^{th}$} & \multicolumn{2}{c}{Max}\\
    \hline
    MARS & $\mathit{6}$&$\mathit{45 \times 10^{-15}}$ & $\mathbf{2}$&$\mathbf{70 \times 10^{-14}}$ & $1$&$66$ & $1$&$96$ & $\mathit{53}$&$\mathit{3}$\\
    SVR & $0$&$0420$ & $0$&$143$ & $0$&$148$ & $\mathit{0}$&$\mathit{860}$ & $119$&$0$\\
    MLP & $0$&$0000689$ & $0$&$0337$ & $\mathbf{0}$&$\mathbf{0795}$ & $\mathbf{0}$&$\mathbf{264}$ & $\mathbf{5}$&$\mathbf{31}$\\
    Delaunay & $\mathbf{0}$&$\mathbf{00}$ & $0$&$187$ & $0$&$919$ & $2$&$72$ & $56$&$3$\\
    ShepMod & $\mathbf{0}$&$\mathbf{00}$ & $0$&$0957$ & $0$&$685$ & $2$&$90$ & $73$&$2$\\
    LSHEP & $\mathbf{0}$&$\mathbf{00}$ & $\mathit{0}$&$\mathit{0153}$ & $\mathit{0}$&$\mathit{106}$ & $1$&$17$ & $113$&$0$\\
    Voronoi & $\mathbf{0}$&$\mathbf{00}$ & $0$&$430$ & $1$&$28$ & $2$&$94$ & $83$&$8$\\
    BoxSpline & $\mathbf{0}$&$\mathbf{00}$ & $0$&$789$ & $2$&$06$ & $5$&$25$ & $119$&$0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-weather}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum value of each column is boldface, while the second lowest
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-weather}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c|}{Min} & \multicolumn{2}{c|}{$25^{th}$} & \multicolumn{2}{c|}{$50^{th}$} & \multicolumn{2}{c|}{$75^{th}$} & \multicolumn{2}{c}{Max}\\
    \hline
    MARS & $5$&$36$ & $3610$&$0$ & $4580$&$0$ & $5450$&$0$ & $13400$&$0$\\
    SVR & $0$&$0138$ & $8$&$47$ & $15$&$4$ & $41$&$9$ & $7700$&$0$\\
    MLP & $0$&$00151$ & $\mathbf{1}$&$\mathbf{60}$ & $\mathbf{3}$&$\mathbf{86}$ & $\mathbf{8}$&$\mathbf{34}$ & $\mathbf{604}$&$\mathbf{0}$\\
    Delaunay & $\mathbf{0}$&$\mathbf{00}$ & $\mathit{2}$&$\mathit{69}$ & $\mathit{13}$&$\mathit{8}$ & $\mathit{35}$&$\mathit{0}$ & $\mathit{4840}$&$\mathit{0}$\\
    ShepMod & $\mathbf{0}$&$\mathbf{00}$ & $4$&$21$ & $17$&$3$ & $51$&$6$ & $6510$&$0$\\
    LSHEP & $1$&$27$ & $199$&$0$ & $260$&$0$ & $343$&$0$ & $6530$&$0$\\
    Voronoi & $\mathit{2}$&$\mathit{89 \times 10^{-10}}$ & $14$&$7$ & $32$&$8$ & $52$&$9$ & $4860$&$0$\\
    BoxSpline & $0$&$00740$ & $20$&$8$ & $40$&$9$ & $79$&$6$ & $7640$&$0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-credit-card}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum value of each column is boldface, while the second lowest
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-credit-card}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \quad\,$0$&$0$ &  & \quad\quad\,\,$22$&$0$ & \quad$0$&$00148$ & \quad\quad\quad$0$&$820$\\
    SVR & $0$&$0$ &  & $1$&$01$ & $\mathit{0}$&$\mathit{000210}$ & $\mathit{0}$&$\mathit{117}$\\
    MLP & $\mathbf{79}$&$\mathbf{5}$ &  & $290$&$0$ & $0$&$000714$ & $0$&$397$\\
    Delaunay & $\mathit{20}$&$\mathit{5}$ &  & $\mathbf{0}$&$\mathbf{000243}$ & $6$&$83$ & $3800$&$$\\
    ShepMod & $0$&$1$ &  & $1$&$45$ & $0$&$000220$ & $0$&$122$\\
    LSHEP & $0$&$0$ &  & $3$&$47$ & $\mathbf{0}$&$\mathbf{000176}$ & $\mathbf{0}$&$\mathbf{0981}$\\
    Voronoi & $0$&$0$ &  & $\mathit{0}$&$\mathit{197}$ & $0$&$0950$ & $52$&$8$\\
    BoxSpline & $0$&$0$ &  & $1$&$66$ & $0$&$000956$ & $0$&$532$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating credit card transaction data
    in Table \ref{table:error-credit-card}. On the right columns are
    median fit time of 5006 points, median time for one approximation,
    and median time approximating 556 points.}
  \label{table:best-credit-card}
\end{table}

>>>>

The forest fire data set \cite{cortez2007data} describes the area of
Montesinho park burned over months of the year along with
environmental conditions. The twelve dimensions being used to model
burn area are the $x$ and $y$ spatial coordinates of burns in the
park, month of year (mapped to $x$, $y$ coordinates on a unit circle),
the FFMC, DMC, DC, and ISI indices (see source for details), the
temperature, relative humidity, wind speed, and outdoor rain. The
original analysis of this data set demonstrated it to be difficult to
model, likely due to the skew in response values.

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.75\textwidth,]{Figures/raw-histogram-throughput.pdf}};
    \node[below=of img, node distance=1cm, yshift=1cm] {I/O Read Throughtput};
    \node[left=of img, node distance=0cm, rotate=90, anchor=center,yshift=-0.7cm] {Count};
  \end{tikzpicture}
  \caption{Histogram of the raw throughput values recorded during all
    IOzone tests across all system configurations. The distribution is
    skewed right, with few tests having significantly higher
    throughput than most others. The data is presented on a $\ln$
    scale.}
  \label{fig:hist-throughput}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l}
    Algorithm & \multicolumn{2}{c|}{Avg. \% Best} & \multicolumn{2}{c|}{\multilinecell{Avg. Fit or \\ Prep. Time (s)}} & \multicolumn{2}{c}{Avg. App. Time (s)}\\
    \hline
    MARS & \quad\quad$4$&$6$ & \,\quad$22$&$3$ & \quad\quad$0$&$00137$\\
    SVR & $\mathit{21}$&$\mathit{1}$ & $0$&$503$ & $\mathit{0}$&$\mathit{000137}$\\
    MLP & $\mathbf{42}$&$\mathbf{1}$ & $210$&$0$ & $0$&$00102$\\
    Delaunay & $6$&$0$ & $\mathbf{0}$&$\mathbf{000143}$ & $3$&$03$\\
    ShepMod & $18$&$4$ & $0$&$711$ & $0$&$000149$\\
    LSHEP & $8$&$4$ & $1$&$69$ & $\mathbf{0}$&$\mathbf{000116}$\\
    Voronoi & $0$&$5$ & $\mathit{0}$&$\mathit{127}$ & $0$&$0375$\\
    BoxSplines & $0$&$2$ & $0$&$816$ & $0$&$000526$\\
  \end{tabular}
  \caption{This average of Appendix Tables
    \ref{table:best-forest-fire}, \ref{table:best-parkinsons},
    \ref{table:best-weather}, and \ref{table:best-credit-card}
    provides a gross summary of overall results. The columns display
    (weighted equally by data set, \textit{not} points) the average
    frequency with which any algorithm provided the lowest absolute
    error approximation, the average time to fit/prepare, and the
    average time required to approximate one point. Interpolants
    provide the lowest error approximation one third of the time
    across all data, while regressors occupy the other two
    thirds. This result is obtained without any customized tuning or
    preprocessing to maximize the performance of any given
    algorithm. In practice, tuning and preprocessing may have large
    effects on approximation performance.}
  \label{table:avg-performance}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c|}{Min} & \multicolumn{2}{c|}{$25^{th}$} & \multicolumn{2}{c|}{$50^{th}$} & \multicolumn{2}{c|}{$75^{th}$} & \multicolumn{2}{c}{Max}\\
    \hline
    MARS & $0$&$00948$ & $9$&$98$ & $20$&$4$ & $32$&$9$ & $863$&$0$\\
    SVR & $0$&$00138$ & $3$&$17$ & $7$&$31$ & $12$&$6$ & $\mathbf{27}$&$\mathbf{5}$\\
    MLP & $0$&$0000239$ & $\mathit{0}$&$\mathit{533}$ & $\mathit{1}$&$\mathit{25}$ & $\mathbf{2}$&$\mathbf{84}$ & $39$&$3$\\
    Delaunay & $\mathit{3}$&$\mathit{72 \times 10^{-12}}$ & $1$&$20$ & $3$&$50$ & $7$&$67$ & $30$&$7$\\
    ShepMod & $\mathbf{0}$&$\mathbf{0}$ & $\mathbf{0}$&$\mathbf{255}$ & $\mathbf{0}$&$\mathbf{908}$ & $\mathit{3}$&$\mathit{43}$ & $34$&$5$\\
    LSHEP & $0$&$00254$ & $2$&$93$ & $7$&$16$ & $13$&$1$ & $\mathit{29}$&$\mathit{0}$\\
    Voronoi & $\mathbf{0}$&$\mathbf{0}$ & $1$&$29$ & $3$&$52$ & $6$&$87$ & $30$&$1$\\
    BoxSpline & $0$&$00287$ & $4$&$39$ & $9$&$10$ & $14$&$8$ & $41$&$3$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-parkinsons}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum of each column is boldface, while the second lowest value
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-parkinsons}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \quad\,$0$&$0$ &  & \quad\quad$37$&$9$ & \quad\,\,$0$&$00253$ & \quad\quad\quad\,\,$1$&$48$\\
    SVR & $0$&$1$ &  & $0$&$859$ & $\mathit{0}$&$\mathit{000181}$ & $\mathit{0}$&$\mathit{106}$\\
    MLP & $\mathit{32}$&$\mathit{0}$ &  & $348$&$0$ & $0$&$00111$ & $0$&$653$\\
    Delaunay & $0$&$0$ &  & $\mathbf{0}$&$\mathbf{000190}$ & $3$&$69$ & $2170$&$0$\\
    ShepMod & $\mathbf{66}$&$\mathbf{4}$ &  & $1$&$13$ & $0$&$000182$ & $0$&$107$\\
    LSHEP & $0$&$0$ &  & $2$&$39$ & $\mathbf{0}$&$\mathbf{000144}$ & $\mathbf{0}$&$\mathbf{0845}$\\
    Voronoi & $1$&$6$ &  & $\mathit{0}$&$\mathit{298}$ & $0$&$0274$ & $16$&$1$\\
    BoxSpline & $0$&$0$ &  & $1$&$26$ & $0$&$000643$ & $0$&$377$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating Parkinson's data in Table
    \ref{table:error-parkinsons}. On the right columns are median fit
    time of 5288 points, median time for one approximation, and median
    time approximating 587 points.}
  \label{table:best-parkinsons}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c|}{Min} & \multicolumn{2}{c|}{$25^{th}$} & \multicolumn{2}{c|}{$50^{th}$} & \multicolumn{2}{c|}{$75^{th}$} & \multicolumn{2}{c}{Max}\\
    \hline
    MARS & $\mathit{6}$&$\mathit{45 \times 10^{-15}}$ & $\mathbf{2}$&$\mathbf{70 \times 10^{-14}}$ & $1$&$66$ & $1$&$96$ & $\mathit{53}$&$\mathit{3}$\\
    SVR & $0$&$0420$ & $0$&$143$ & $0$&$148$ & $\mathit{0}$&$\mathit{860}$ & $119$&$0$\\
    MLP & $0$&$0000689$ & $0$&$0337$ & $\mathbf{0}$&$\mathbf{0795}$ & $\mathbf{0}$&$\mathbf{264}$ & $\mathbf{5}$&$\mathbf{31}$\\
    Delaunay & $\mathbf{0}$&$\mathbf{0}$ & $0$&$187$ & $0$&$919$ & $2$&$72$ & $56$&$3$\\
    ShepMod & $\mathbf{0}$&$\mathbf{0}$ & $0$&$0957$ & $0$&$685$ & $2$&$90$ & $73$&$2$\\
    LSHEP & $\mathbf{0}$&$\mathbf{0}$ & $\mathit{0}$&$\mathit{0153}$ & $\mathit{0}$&$\mathit{106}$ & $1$&$17$ & $113$&$0$\\
    Voronoi & $\mathbf{0}$&$\mathbf{0}$ & $0$&$430$ & $1$&$28$ & $2$&$94$ & $83$&$8$\\
    BoxSpline & $\mathbf{0}$&$\mathbf{0}$ & $0$&$789$ & $2$&$06$ & $5$&$25$ & $119$&$0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-weather}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum value of each column is boldface, while the second lowest
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-weather}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c|}{Min} & \multicolumn{2}{c|}{$25^{th}$} & \multicolumn{2}{c|}{$50^{th}$} & \multicolumn{2}{c|}{$75^{th}$} & \multicolumn{2}{c}{Max}\\
    \hline
    MARS & $5$&$36$ & $3610$&$0$ & $4580$&$0$ & $5450$&$0$ & $13400$&$0$\\
    SVR & $0$&$0138$ & $8$&$47$ & $15$&$4$ & $41$&$9$ & $7700$&$0$\\
    MLP & $0$&$00151$ & $\mathbf{1}$&$\mathbf{60}$ & $\mathbf{3}$&$\mathbf{86}$ & $\mathbf{8}$&$\mathbf{34}$ & $\mathbf{604}$&$\mathbf{0}$\\
    Delaunay & $\mathbf{0}$&$\mathbf{0}$ & $\mathit{2}$&$\mathit{69}$ & $\mathit{13}$&$\mathit{8}$ & $\mathit{35}$&$\mathit{0}$ & $\mathit{4840}$&$\mathit{0}$\\
    ShepMod & $\mathbf{0}$&$\mathbf{0}$ & $4$&$21$ & $17$&$3$ & $51$&$6$ & $6510$&$0$\\
    LSHEP & $1$&$27$ & $199$&$0$ & $260$&$0$ & $343$&$0$ & $6530$&$0$\\
    Voronoi & $\mathit{2}$&$\mathit{89 \times 10^{-10}}$ & $14$&$7$ & $32$&$8$ & $52$&$9$ & $4860$&$0$\\
    BoxSpline & $0$&$00740$ & $20$&$8$ & $40$&$9$ & $79$&$6$ & $7640$&$0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-credit-card}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum value of each column is boldface, while the second lowest
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-credit-card}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \quad\,$0$&$0$ &  & \quad\quad\,\,$22$&$0$ & \quad$0$&$00148$ & \quad\quad\quad$0$&$820$\\
    SVR & $0$&$0$ &  & $1$&$01$ & $\mathit{0}$&$\mathit{000210}$ & $\mathit{0}$&$\mathit{117}$\\
    MLP & $\mathbf{79}$&$\mathbf{5}$ &  & $290$&$0$ & $0$&$000714$ & $0$&$397$\\
    Delaunay & $\mathit{20}$&$\mathit{5}$ &  & $\mathbf{0}$&$\mathbf{000243}$ & $6$&$83$ & $3800$&$0$\\
    ShepMod & $0$&$1$ &  & $1$&$45$ & $0$&$000220$ & $0$&$122$\\
    LSHEP & $0$&$0$ &  & $3$&$47$ & $\mathbf{0}$&$\mathbf{000176}$ & $\mathbf{0}$&$\mathbf{0981}$\\
    Voronoi & $0$&$0$ &  & $\mathit{0}$&$\mathit{197}$ & $0$&$0950$ & $52$&$8$\\
    BoxSpline & $0$&$0$ &  & $1$&$66$ & $0$&$000956$ & $0$&$532$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating credit card transaction data
    in Table \ref{table:error-credit-card}. On the right columns are
    median fit time of 5006 points, median time for one approximation,
    and median time approximating 556 points.}
  \label{table:best-credit-card}
\end{table}
